Paper_text_working_file

### 2019-04-29 Paper_markdown.Rmd
Most statistical tests done. Need to create plots and double check against original STATA output.

install.packages("tidyverse")
install.packages("DataCombine")

library(plyr)
library(tidyverse)
library(DataCombine)
library(haven)

@@

#mergin in dyadic mid data
Master2 <- full_join(Master, Dyadic_MID, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))

@@

Master3 <- filter(Master2, ccodea != 2, ccodeb != 2, year <= 2012, year >= 1949)

@@

#Creating variable identifying joint democracy
Master3 <- Master3 %>%
    mutate(Joint_Dem = ifelse(politya >= 6 & polityb >=6, 1, 0))
head(Master3$Joint_Dem, 1000)

#Creating variable identifying if at least one member of the dyad is a major power.
Master3 <- Master3 %>%
    mutate(Joint_Dem = ifelse(majpow1 == 1 | majpow2 == 1, 1, 0))
head(Master3$Joint_Dem, 1000)

@@

>>>>

install.packages("tidyverse")
install.packages("DataCombine")
install.packages("dotwhisker")

library(plyr)
library(tidyverse)
library(DataCombine)
library(haven)
library(dotwhisker)

options(digits = 4)

@@

#mergin in dyadic mid data
Master2 <- full_join(Master, Dyadic_MID, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
summary(Master2$year)

@@

Master3 <- filter(Master2, ccodea != 2, ccodeb != 2, year < 2012, year >= 1950)

#Variable Generation

@@

#Creating variable identifying joint democracy
Master3 <- Master3 %>%
    mutate(Joint_Dem = ifelse(polity2a >= 6 & polity2b >=6, 1, 0))
head(Master3$Joint_Dem, 1000)

#Creating variable identifying if at least one member of the dyad is a major power.
Master3 <- Master3 %>%
    mutate(Major = ifelse(majpow1 == 1 | majpow2 == 1, 1, 0))
head(Master3$Major, 1000)

@@

#Binary variable identifying if the dyad year is during or after the Cold War
Master3 <- Master3 %>%
    mutate(Post_Cold_War = ifelse(year > 1990, 1, 0))

Master3 <- Master3 %>%
    mutate(Hostility = 0) %>%
    Hostility[hihost == 2] <- 1 %>%
    Hostility[hihost == 3] <- 2 %>%
    Hostility[hihost == 4] <- 3 %>%
    Hostility[hihost == 5] <- 4 %>%
    Hostility[ifelse(is.na(hihost))] <- 0

Master3 <- Master3 %>%
  rename(
    Contiguous = contig,
  )

Master4 <- select(Master3, year, Mid, Use_Force, US_Naval_Cap, Same_Region, Contiguous, Ally, Joint_Dem, Relative_Cap, Major, Post_Cold_War)
summary(Master4)

#Statistical Tests

#Bivariate Logits
MID_BI_Log <- glm(Mid ~ US_Naval_Cap, data = Master4, family=binomial)
summary(MID_BI_Log)
dwplot(MID_BI_Log)

Force_BI_Log <- glm(Use_Force ~ US_Naval_Cap, data = Master4, family=binomial)
summary(Force_BI_Log)
dwplot(Force_BI_Log)

#Full Models
  #Logistic regression
MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Same_Region + Contiguous + Ally + Joint_Dem + Relative_Cap + Major + Post_Cold_War, data = Master4)
summary(MID_Full_Log)
dwplot(MID_Full_Log)

Force_Full_Log <- glm(Use_Force ~ US_Naval_Cap + Same_Region + Contiguous + Ally + Joint_Dem + Relative_Cap, data = Master4)
summary(Force_Full_Log)
dwplot(Force_Full_Log)

  #Mlogit model
Hostility_Mlog <- mlogit(Hostility ~ US_Naval_Cap + Same_Region + Contiguous + Ally + Joint_Dem + Relative_Cap, data = Master4, reflevel = 0)
summary(Hostility_Mlog)
dwplot(Hostility_Mlog)

  #Heckman model
